screeningAnalysis

### 2024-02-15 screenCode.Rmd
loaded data only to check equal participants between conditions

# Rename the "Duration..in.seconds." column to "duration"
names(df_screening)[names(df_screening) == "Duration..in.seconds."] <- "duration"

# Step 2: Filter rows
df_screening <- df_screening[df_screening$Q1 == "I accept" & !grepl('test', df_screening$Q2) & df_screening$DistributionChannel ==  'anonymous', ]
cat("valid submissions: ",  nrow(df_screening), "\n")

@@

>>>>

# Rename the "Duration..in.seconds." column to "duration"
names(df_screening)[names(df_screening) == "Duration..in.seconds."] <- "duration"
names(df_screening)[names(df_screening) == "Q2"] <- "id"

# Step 2: Filter rows
df_screening <- df_screening[df_screening$Q1 == "I accept" & !grepl('test', df_screening$id) & df_screening$DistributionChannel ==  'anonymous', ]
cat("valid submissions: ",  nrow(df_screening), "\n")

@@

# Save the df_screening data frame to a file named "df_screening.RData"
save(df_screening, file = "data/df_screening.RData")

#DUPLICATES?
```{r}
library(dplyr)

# Find duplicates based on 'id'
duplicates <- df_screening %>%
  group_by(id) %>%
  summarize(count = n(), .groups = 'drop') %>%
  filter(count > 1)

# View the duplicates and their counts
print(duplicates)
